ZPY: Open Source Synthetic Data for Computer Vision

### 2021-06-24 docs/paper/paper.tex
more content

Blender allows for user-created AddOns, and provides tooling for integrating addon functionality with the Blender UI.

Popular AddOns include X, X, and X.

Those who use Blender in their 3D workflow are

@@

Abstracting away the difficulties of the cloud workflow and providing an intuitive and convenient interface for parallelizing computation is thus important for the democratization of deep learning and synthetic data workflows. Much like platforms have emerged for the training and tuning workflows of deep learning, an opportunity exists to create platforms for the generation and tuning workflows of synthetic data.

@@

We provide three different interfaces to interact with our product: a Python API \ref{lst:api}, a CLI \ref{lst:cli}, and a graphical WebApp \ref{fig:webapp}. Power users want an API (application programming interface) and CLI (command line interface). Building a ramp for the bulk of the developer community requires a GUI

>>>>

Blender allows for user-created AddOns, and provides tooling for integrating addon functionality with the Blender UI. Examples of popular AddOns are NodeWrangler and Botaniq. NodeWrangler adds simple productivity functionality to the Node System, a method of visual scripting common to 3D tools. Botaniq is a library of tree and plant assets, with a built in scattering method hugely popular due to the complexity of creating grass and trees from scratch. Blender users are comfortable installing and using addons as part of their workflow. The zpy-addon allows for mouse and button based versions of the segmentation, sim run script execution, and sim exporting workflows. Though these actions are possible entirely through python code, providing convenient button versions in a UI makes these processes available to a larger community of 3D artists who are not as comfortable in a code-only environment.

@@

Abstracting away the difficulties of the cloud workflow and providing an intuitive and convenient interface for parallelizing computation is thus important for the synthetic data workflow. Dataset generation jobs can be made with the zpy CLI and API such that many computers are used, thus speeding up the generation job.

@@

We provide three different interfaces to interact with our product: a Python API \ref{lst:api}, a CLI \ref{lst:cli}, and a graphical WebApp \ref{fig:webapp}. Power users want an API (application programming interface) and CLI (command line interface). Building a ramp for the bulk of the developer community requires a GUI.
